---
title: "AirBNB Guest Satisfaction Factors"
author: "MJ"
date: "3/16/2018"
output: html_document
---

```{r setup, include=FALSE}
require(knitr)
require(abd)
library(dplyr)
library(sf)
test <- st_read("/Users/maraljamali/Desktop/My_Lovely_DS_Project/Ward_from_2012/ward_from_2012.shp")
#map(test)
```
## R Markdown
1. Airbnb

 Question: What factors drive Airbnb guest  satisfaction?

Airbnb guest satisfaction rate and their proximity to Points Of Interests (POI) with positive reviews on yelp. 
Is there a meaningful relationship between the guest satisfaction rate and the host’s proximity to well reviewed pois? Is there a meaningful relationship between the guest satisfaction rate and neighborhood safety?

Relationship between crime and airbnb guest satisfaction
Relationship between POIs and airbnb guest satisfaction


```{r}
library(dplyr)
#Quick look at the dc_crime dataset
df_crime <- read.csv("/Users/maraljamali/Desktop/My_Lovely_DS_Project/dc_crime.csv", header=TRUE)
df <- as.data.frame(df)
head(df,5)
#Quick look at the Airbnb dataset
df_air1 <- read.csv("/Users/maraljamali/Desktop/My_Lovely_DS_Project/DC_Airbnb/washington/airbnb_1.csv", header=TRUE)
df_air2 <- read.csv("/Users/maraljamali/Desktop/My_Lovely_DS_Project/DC_Airbnb/washington/airbnb_2.csv", header=TRUE)
df_air3 <- read.csv("/Users/maraljamali/Desktop/My_Lovely_DS_Project/DC_Airbnb/washington/airbnb_3.csv", header=TRUE)
df_air1 <- as.data.frame(df_air1)
df_air2 <- as.data.frame(df_air2)
airbnb_first2 <- rbind(df_air1, df_air2)
head(airbnb_first2, 5)
#Quick look at the yelp dataset
df_yelp <- read.csv("/Users/maraljamali/Desktop/My_Lovely_DS_Project/yelp_dataset/yelp_review.csv", header = TRUE)
df_yelp <- as.data.frame(df_yelp)
head(df_yelp, 5)
#Washington DC Shapefile

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
